Sound Automated Synthesis of Digital Controllers

### 2016-10-10 paper/paper.tex
Call it a day

The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$ 
are represented by the following z-expression:
%
\begin{equation}
\label{satellite-b2}
C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
\end{equation} 
%
\begin{equation}
\label{satellite-c2}
C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
\end{equation}

>>>>

The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$,discretized with sample time equal to $1 s$ and $2 s$ respectively, 
are represented by the following z-expression:
%
\begin{equation}
\label{satellite-b2}
C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
\end{equation} 
%
\begin{equation}
\label{satellite-c2}
C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
\end{equation}
